### 2018-11-21 Sections/physical_architectures_for_quantum_computing.tex
Edit qubus

The computation therefore proceeds as alternating applications of: (1) measuring the leftmost column of physical qubits to evolve the computation by a single step; (2) bond on a new column of qubits to the rightmost column. The qubits in between the left and rightmost columns act as a buffer to give us some leeway when bonding operations fail. The architecture is shown in Fig.~\ref{fig:on_demand_cs}.

@@

\begin{figure*}[!htpb]
	\includegraphics[clip=true, width=\textwidth]{weak_ck_parity_gate}
\caption{Construction of a 2-mode, polarisation-encoded, photonic parity gate using an ancillary qubus coherent state, mediating photonic interactions via weak cross-Kerr non-linearities.}\label{fig:weak_ck_parity}	
\end{figure*}

>>>>

The computation therefore proceeds as alternating applications of:
\begin{enumerate}
	\item Measure the leftmost column of physical qubits to evolve the computation by a single step.
	\item Bond on a new column of qubits to the rightmost column.
\end{enumerate}
The qubits in between the left and rightmost columns act as a buffer to give us some leeway when bonding operations fail. The architecture is shown in Fig.~\ref{fig:on_demand_cs}.

@@

\begin{figure*}[!htpb]
	\includegraphics[clip=true, width=\textwidth]{weak_ck_parity_gate}
\caption{Construction of a 2-mode, polarisation-encoded, photonic parity gate using an ancillary qubus coherent state $\ket\alpha$, mediating entangling photonic interactions between $\ket{\psi_a}$ and $\ket{\psi_b}$ via weak cross-Kerr non-linearities (denoted by the controlled-$\theta$ gates). The polarising beamsplitters\index{Polarising beamsplitters} are used to switch between polarisation and dual-rail encoding. The qubus is an optical channel, potentially across long distances for performing distributed gates. The measurement $M$ is a homodyne measurement\index{Homodyne measurements}, which feedforwards to a phase correction.}\label{fig:weak_ck_parity}	
\end{figure*}
